---
title: "Exploratory Data Analysis & Confirmatory Data Analysis"
author: "Walaiporn Pawitranon"
---

# 1. Overview

## 1.1 Project Brief

Take-home exercise 2 is a preliminary work of the final group project - Customer behavior in Latin American Fintech. In the financial technology (Fintech) industry, understanding customer behavior and identifying factors that influence customer retention and churn have become increasingly important. High customer churn can negatively affect business sustainability and profitability, raising concerns among fintech companies about how to improve customer satisfaction, engagement, and loyalty. Therefore, effective data analysis and visualization are essential to help (1) identify patterns and trends in customer behavior and (2) understand the key factors associated with customer churn.

The project team consists of three members, and each member will take one of the main prototype modules as follows:

-   Exploratory Data Analysis & Confirmatory Data Analysis

-   Cluster Analysis

-   Decision Tree Analysis

## 1.2 Project Objective

The project will be using data from *A comprehensive dataset of customer behavior in Latin American Fintech: 12-month transactional and demographic data for churn analysis* paper. The objective of my assignment is to build a prototype - user interface (UI) design on **Exploratory Data Analysis & Confirmatory Data Analysis** that provides easy-to-use and insightful visualisation tools.

# 2. Data Preparation

## 2.1 Overview of the Data

The dataset contains information on 48,723 customers of a Colombian fintech company, collected over a 12-month period from January 4, 2023, to December 29, 2023. The 48,723 customers represent the complete active customer base for calendar year 2023, making this a comprehensive population study rather than a sample.

The dataset comprises 57 variables categorized into demographics, product usage, transaction records, customer feedback, digital engagement, and derived metrics.

Data are organized in two CSV files with relational structure:

1.  **customer_data.csv:** Contains customer-level information including demographics, product portfolio, satisfaction metrics, and aggregated behavioral features (one row per customer, 48,723 rows).

2.  **transactions_data.csv:** Contains transaction-level data for all customers over the 12-month period (one row per transaction, 3,159,157 rows).

## 2.2 Install and Launch R Packages

The project uses `p_load()` of pacman package to check if the R packages are installed in the computer.

The following code chunk is used to install and launch the R packages.

```{r}
pacman::p_load(dplyr,tidyr,ggplot2,readxl,scales,ggstatsplot,patchwork,lubridate, readr)
```

## 2.3 Import Data

The project will examine *A comprehensive dataset of customer behavior in Latin American Fintech*. There are 2 files which are

```{r}
customer <- read.csv("data/customer_data.csv", na.strings = c("", "NA"))
```

```{r}
transaction <- read.csv("data/transactions_data.csv")
```

## 2.4 Data Cleaning

### 2.4.1 Handling missing value

To examine missing values for each variable individually, the code chunk below was used to compute the number of missing observations by column.

```{r}
colSums(is.na(customer))
```

After inspecting the dataset using c`olSums(is.na(customer))`, only ‘complaint_topics’ (49.97%), ‘credit_utilization_ratio’ (37.48%), and ‘feature_requests’ (33.07%) contain missing values when the corresponding product or interaction is not applicable.

These columns will be dropped using the code chunk below.

```{r}
customer <- customer %>% select(-credit_utilization_ratio)
customer <- customer %>% select(-feature_requests)
customer <- customer %>% select(-complaint_topics)
```

### 2.4.2 Check Data Duplication

For the customer dataset, it is necessary to verify whether the `customer_id` values are duplicated. Each customer should have a unique identifier to ensure data accuracy and consistency.

```{r}
sum(duplicated(customer$customer_id))
```

### 2.4.3 Correct Data Type

#### 2.4.3.1 Check Data Type of Each Column

Checking the data type of each column in a dataset is an essential step in data preprocessing. Different types of analyses and operations require variables to be in the correct format by using the code chunk below.

```{r}
str(customer)
```

#### 2.4.3.2 Correct the data type

The Code chunk below is ot change data type of the variables that have incorrect data type

-   Customer data

```{r}
customer$customer_id <- as.character(customer$customer_id)

customer$first_tx<- as.Date(customer$first_tx)

customer$last_tx <- as.Date(customer$last_tx)

customer$last_survey_date <- as.Date(customer$last_survey_date)

customer$last_transaction_date <- as.Date(customer$last_transaction_date)

customer$first_transaction_date <- as.Date(customer$first_transaction_date)
```

-   Transaction data

```{r}
transaction$date <- as.Date(transaction$date)

transaction <- transaction %>%
  mutate(
    year_month = floor_date(date, "month"),
    year = year(date),
    month = month(date, label = TRUE)
  )
```

#### 2.4.3.3 Recoding categorical variables

Although many variables in the dataset are recorded using numerical codes (e.g., 1–5), these values do not represent actual quantities or measurements but instead correspond to ordered categories or levels of perception. If left as numeric variables, R would treat them as continuous numbers. Therefore, these variables need to be recoded as ordered factors with meaningful labels to ensure accurate and appropriate analysis and visualization by using the code chunk below.

```{r}
customer <- customer |>
  mutate(
    active_products = factor(active_products,
                  levels = c(0,1,2,3,4,5),
                  labels = c("0 product",
                             "1 product",
                             "2 products",
                             "3 products",
                             "4 products",
                             "5 products")),
    satisfaction_score = factor(satisfaction_score,
                  levels = c(2,3,4,5,6),
                  labels = c("Very low",
                             "Low",
                             "Medium",
                             "High",
                             "Very high")),
    app_logins_group = cut(app_logins_frequency,
      breaks = c(0,25,50,100),
      labels = c("Rarely","Often","Always"),
      include.lowest = TRUE))


```

### 2.4.4 Check logic Consistency

Churn_probability should be in \[0,1\] satsfaction_core must in the range \[1,6\]

```{r}
summary(customer)
```

# 3. Exploratory Data Analysis

## 3.1 Check correlation

As a first step in the Exploratory Data Analysis (EDA), correlation analysis is performed to examine the relationships between numerical variables in the dataset. Checking correlations helps identify whether variables are positively or negatively related and how strongly they are associated with each other.

```{r, fig.width=10, fig.height=8}
#| echo: true
#| code-fold: true
#| code-summary: "Code" 

library(corrplot)
corr_matrix <- cor(customer[, sapply(customer, is.numeric)])
corrplot(corr_matrix, method = "color")
```

## 3.2 Customer Profile Overview

The dashboard was developed in R using the `ggplot2`, `dplyr`, and `patchwork` packages. Key performance indicators (KPIs), including total customers, average age, and average household size, were calculated using `nrow()` and `mean()`.

A KPI summary panel was created using `ggplot()` and `annotate()` to display the calculated metrics as text.

For categorical variables such as gender, income bracket, customer segment, and acquisition channel, the `count()` function was used to aggregate frequencies. These results were visualized using bar charts with `geom_bar(stat = "identity")`.

```{r, fig.width=10, fig.height=6}
#| echo: true
#| code-fold: true
#| code-summary: "Code"

total_customers <- nrow(customer)
avg_age <- round(mean(customer$age), 1)
avg_household <- round(mean(customer$household_size), 1)

kpi_plot <- ggplot() +
  annotate("text", x = 1, y = 3,
           label = paste("Total Customers:", total_customers),
           size = 5) +
  annotate("text", x = 1, y = 2,
           label = paste("Average Age:", avg_age),
           size = 5) +
  annotate("text", x = 1, y = 1,
           label = paste("Avg Household Size:", avg_household),
           size = 5) +
  xlim(0, 2) + ylim(0, 4) +
  theme_void()

gender_plot <- customer %>%
  count(gender) %>%
  ggplot(aes(x = gender, y = n)) +
  geom_bar(stat = "identity",fill = "darkgreen") +
  theme_minimal() +
  labs(title = "Gender Distribution",
       x = "Gender", y = "Count")

income_plot <- customer %>%
  count(income_bracket) %>%
  ggplot(aes(x = income_bracket, y = n)) +
  geom_bar(stat = "identity", fill = "orange") +
  theme_minimal() +
  labs(title = "Income Distribution",
       x = "Income", y = "Count") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

segment_plot <- customer %>%
  count(customer_segment) %>%
  ggplot(aes(x = customer_segment, y = n)) +
  geom_bar(stat = "identity", fill = "purple") +
  theme_minimal() +
  labs(title = "Customer Segment",
       x = "Segment", y = "Count")

acquisition_plot <- customer %>%
  count(acquisition_channel) %>%
  ggplot(aes(x = acquisition_channel, y = n)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  theme_minimal() +
  labs(title = "Acquisition Channel",
       x = "Channel", y = "Count")

kpi_plot /(gender_plot | income_plot) /(segment_plot | acquisition_plot)
```

::: {.callout-tip title="Insight"}
This dashboard provides a high-level overview of the customer base. The company primarily serves middle-income, middle-aged customers with balanced gender distribution. Most users are occasional or regular users, indicating significant potential to increase engagement. Organic and referral channels are the strongest acquisition drivers, suggesting strong brand presence and customer advocacy.
:::

## 3.3 Transaction Pattern

The transaction data was aggregated at a monthly level to analyze seasonal patterns and transaction trends. Using the `group_by()` function, transactions were grouped by both transaction type and month (`year_month`). For each group, two metrics were calculated: total transaction count (`n()`) and total transaction amount (`sum(amount, na.rm = TRUE)`)

The dataset was then separated into four transaction categories: Transfer, Payment, Withdrawal, and Deposit. For each category, a scaling factor was computed by dividing the maximum transaction count by the maximum transaction amount. This scaling factor was used to align transaction amounts with transaction counts on a secondary y-axis, allowing both metrics to be visualized simultaneously in a single chart.

```{r, fig.width=10, fig.height=6}
#| echo: true
#| code-fold: true
#| code-summary: "Code"

monthly_type <- transaction %>%
  group_by(type, year_month) %>%
  summarise(
    transaction_count = n(),
    transaction_amount = sum(amount, na.rm = TRUE),
    .groups = "drop"
  )

transfer_data <- monthly_type %>%
  filter(type == "Transfer")

payment_data <- monthly_type %>%
  filter(type == "Payment")

withdrawal_data <- monthly_type %>%
  filter(type == "Withdrawal")

deposit_data <- monthly_type %>%
  filter(type == "Deposit")

scale_factor_t <- max(transfer_data$transaction_count) / 
                max(transfer_data$transaction_amount)

scale_factor_p <- max(payment_data$transaction_count) / 
                max(payment_data$transaction_amount)

scale_factor_w <- max(withdrawal_data$transaction_count) / 
                max(withdrawal_data$transaction_amount)

scale_factor_d <- max(deposit_data$transaction_count) / 
                max(deposit_data$transaction_amount)

transfer <- ggplot(transfer_data, aes(x = year_month)) +
  
  # Count (Primary axis)
  geom_line(aes(y = transaction_count), linewidth = 1) +
  geom_point(aes(y = transaction_count)) +
  
  # Amount (Scaled)
  geom_line(aes(y = transaction_amount * scale_factor_t),
            linetype = "dashed",
            linewidth = 1) +
  
  scale_y_continuous(
    name = "Transaction Count",
    
    sec.axis = sec_axis(
      ~ . / scale_factor_t,
      name = "Transaction Amount"
    )
  ) +
  
  scale_x_date(
    date_breaks = "1 month",
    date_labels = "%b %Y"
  ) +
  
  labs(
    title = "Monthly Transaction Count and Amount - Transfer",
    x = "Month"
  ) +
  
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))


payment <- ggplot(payment_data, aes(x = year_month)) +
  
  # Count (Primary axis)
  geom_line(aes(y = transaction_count), linewidth = 1) +
  geom_point(aes(y = transaction_count)) +
  
  # Amount (Scaled)
  geom_line(aes(y = transaction_amount * scale_factor_p),
            linetype = "dashed",
            linewidth = 1) +
  
  scale_y_continuous(
    name = "Transaction Count",
    
    sec.axis = sec_axis(
      ~ . / scale_factor_p,
      name = "Transaction Amount"
    )
  ) +
  
  scale_x_date(
    date_breaks = "1 month",
    date_labels = "%b %Y"
  ) +
  
  labs(
    title = "Monthly Transaction Count and Amount - Payment",
    x = "Month"
  ) +
  
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))


withdrawal <- ggplot(withdrawal_data, aes(x = year_month)) +
  
  # Count (Primary axis)
  geom_line(aes(y = transaction_count), linewidth = 1) +
  geom_point(aes(y = transaction_count)) +
  
  # Amount (Scaled)
  geom_line(aes(y = transaction_amount * scale_factor_w),
            linetype = "dashed",
            linewidth = 1) +
  
  scale_y_continuous(
    name = "Transaction Count",
    
    sec.axis = sec_axis(
      ~ . / scale_factor_w,
      name = "Transaction Amount"
    )
  ) +
  
  scale_x_date(
    date_breaks = "1 month",
    date_labels = "%b %Y"
  ) +
  
  labs(
    title = "Monthly Transaction Count and Amount - Withdrawal",
    x = "Month"
  ) +
  
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

deposit <- ggplot(deposit_data, aes(x = year_month)) +
  
  # Count (Primary axis)
  geom_line(aes(y = transaction_count), linewidth = 1) +
  geom_point(aes(y = transaction_count)) +
  
  # Amount (Scaled)
  geom_line(aes(y = transaction_amount * scale_factor_d),
            linetype = "dashed",
            linewidth = 1) +
  
  scale_y_continuous(
    name = "Transaction Count",
    
    sec.axis = sec_axis(
      ~ . / scale_factor_d,
      name = "Transaction Amount"
    )
  ) +
  
  scale_x_date(
    date_breaks = "1 month",
    date_labels = "%b %Y"
  ) +
  
  labs(
    title = "Monthly Transaction Count and Amount - Deposit",
    x = "Month"
  ) +
  
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))


(transfer+payment) / (withdrawal+deposit)
```

::: {.callout-tip title="Insight"}
The transaction pattern analysis reveals:

-   Transfer transactions dominate in volume and consistency, with visible peaks around mid-year and early Q4. Seasonal spikes may be linked to business cycles or major financial periods (e.g., mid-year or year-end financial planning).

-   Payment and Deposit categories show stronger seasonal fluctuations, with clear increases in mid-year months.

-   Withdrawal activity is comparatively stable.

-   Deposits show periodic increases in both count and transaction amount, particularly during mid-year and late-year months.

-   Peaks in transaction amount often coincide with peaks in transaction count, suggesting synchronized behavioral patterns rather than isolated high-value transactions.

These findings support the presence of seasonality and provide a strong foundation for further time-series analysis, customer segmentation, and predictive modeling.
:::

## 3.4 Digital Engagement Analysis

The Digital Engagement dashboard was developed using `ggplot2` to summarize user activity, engagement behavior, and retention-related metrics.

The key engagement KPIs were calculated, including total users (`nrow()`), average app login frequency, average monthly transaction count, and average churn probability (formatted as percentage). These metrics provide a high-level overview of platform engagement and customer sentiment.

Several visualizations are used to explore relationships in the data. `geom_point()` creates scatter plots to examine the relationships between app login frequency and churn probability, and between monthly transaction count and total transaction volume, while a regression line `(geom_smooth(method = "lm"))` highlights the overall trend between engagement and churn risk. In addition, `geom_boxplot()` is used to show the distribution of feature usage diversity across different satisfaction score levels.

```{r, fig.width=10, fig.height=8}
#| echo: true
#| code-fold: true
#| code-summary: "Code"
#| 
total_users <- nrow(customer)
avg_logins <- round(mean(customer$app_logins_frequency, na.rm = TRUE),1)
avg_tx_freq <- round(mean(customer$monthly_transaction_count, na.rm = TRUE),2)

kpi_plot <- ggplot() +
  annotate("text", x=1, y=5, label=paste("Total Users:", total_users), size=5) +
  annotate("text", x=1, y=4, label=paste("Avg Logins:", avg_logins), size=5) +
  annotate("text", x=1, y=3, label=paste("Avg Monthly Transaction:", avg_tx_freq), size=5) +
  xlim(0,2) + ylim(0,6) +
  theme_void()

login_churn_plot <- ggplot(customer, aes(x = app_logins_frequency, y = churn_probability)) +
        geom_point(alpha = 0.6, color = "#2C7FB8") +
        geom_smooth(method = "lm", se = FALSE, color = "red") +
        theme_minimal() +
        labs(title = "Relationship Between App Login Frequency and Churn")

feature_sat_plot <- ggplot(customer, aes(x = satisfaction_score, y = feature_usage_diversity))+
        geom_boxplot() +
        theme_minimal() +
        labs(title = "Distribution of Feature Usage by Satiafaction Score")

transaction_plot <- ggplot(customer,
       aes(x = monthly_transaction_count,
           y = total_transaction_volume)) +
  geom_point() +
  theme_minimal() +
  labs(title="Transaction Frequency vs Volume",
       x="Monthly Transaction Count",
       y="Total Transaction Volume")

kpi_plot /(login_churn_plot | feature_sat_plot) / transaction_plot

```

::: {.callout-tip title="Insight"}
-   The relationship between app login frequency and churn probability shows a negative trend. Customers who log into the app more frequently tend to have lower churn probability, suggesting that higher engagement is associated with better customer retention.

-   The feature usage diversity increases with higher satisfaction levels. Customers with very high satisfaction scores tend to use more app features, as shown by the higher median and wider distribution in the boxplot.

-   The Transaction Frequency vs Volume plot shows a positive relationship between transaction count and total transaction volume.
:::

## 3.5 Customer Experience

In this section, customer experience is analyzed by examining key metrics and relationships between engagement, satisfaction, feedback, and churn. The average churn probability provides a high-level overview of overall customer retention risk. Several visualizations are used to explore these relationships: `geom_boxplot()` illustrates how satisfaction relates to app login frequency and churn probability, `geom_point()` shows the relationship between churn probability and customer lifetime value (CLV), and `geom_tile()` visualizes the relationship between feedback sentiment and satisfaction score. Together, these visualizations help identify patterns in customer behavior and highlight factors associated with customer experience and churn risk.

```{r, fig.width=10, fig.height=8}
#| echo: true
#| code-fold: true
#| code-summary: "Code"

avg_churn <- percent(mean(customer$churn_probability, na.rm = TRUE))

kpi_plot <- ggplot() +
  annotate("text", x=1, y=2, label=paste("Avg Churn Probability:", avg_churn), size=5) +
  theme_void()

engagement_satisfaction_plot <- ggplot(customer,
       aes(x =satisfaction_score,
           y = app_logins_frequency)) +
  geom_boxplot() +
  theme_minimal() +
  labs(title="Satisfaction VS Engagement",
       x="Satisfaction Score",
       y="App Login Frequency")

churn_plot <- ggplot(customer,
       aes(x = churn_probability,
           y = customer_lifetime_value)) +
  geom_point() +
  theme_minimal() +
  labs(title="Churn Probability vs CLV",
       x="Churn Probability",
       y="Customer Lifetime Value")


x <- "feedback_sentiment"
y <- "satisfaction_score"

df <- customer %>%
  count(.data[[x]], .data[[y]])

feedback_plot <- ggplot(df,
            aes_string(x = x, y = y, fill = "n")) +
  geom_tile() +
  scale_fill_gradient(low = "white", high = "steelblue") +
  theme_minimal() +
  labs(title = "Feedback Sentiment VS Satisfaction Score")

satisfaction_churn_plot <- ggplot(customer,
       aes(x = satisfaction_score,
           y = churn_probability)) +
  geom_boxplot() +
  theme_minimal() +
  labs(title="Satisfaction VS Churn Probability",
       x="Satisfaction Score",
       y="Churn Probability")

kpi_plot /(engagement_satisfaction_plot + churn_plot)/ ( feedback_plot + satisfaction_churn_plot)

```

::: {.callout-tip title="Insight"}
-   The average churn probability across all customers is 34%, indicating a significant portion of the customer base is at risk of leaving.

-   Customer engagement, measured by app login frequency, is positively associated with satisfaction: more frequent logins tend to correspond with higher satisfaction scores.

-   The churn probability vs. CLV plot shows that most customers have moderate churn probability, but those with higher churn probability generally have lower customer lifetime value (CLV).

-   The Feedback sentiment VS Satisfaction score shows that positive feedback related to higher satisfaction score.

-   The Satisfaction VS Churn Probability shows that the higher satsfaction score result in lower churn probability.
:::

## 3.6 Geographical Distribution of Customers

The code chunk below will be used to install and load package for handling geospatial data in RStudio

```{r}
pacman::p_load(sf, tmap)
```

### 3.6.1 Importing Geospatial Data into R

The code chunk below uses the `st_read()` function of sf package to import gadm41_COL_1 shapefile into R as a simple feature data frame

```{r}
mpsz <- st_read(dsn = "data/geospatial", 
                layer = "gadm41_COL_1")
```

Examine the content of mpsz by using the code chunk below.

```{r}
mpsz
```

### 3.6.2 Joining the attribute data and geospatial data

This code prepares customer location data and joins it with the geographic shapefile of Colombian departments in order to visualize the geographical distribution of customers.

```{r}
#| echo: true
#| code-fold: true
#| code-summary: "Code"

library(dplyr)
library(sf)
library(stringi)

customer <- customer %>%
  mutate(
    department = stri_trim_both(stri_extract_first_regex(location, "(?<=, ).*")),
    department_clean = stri_trans_general(department, "Latin-ASCII")
  )

dept_customer <- customer %>%
  group_by(department_clean) %>%
  summarise(no_customers = n())

mpsz <- mpsz %>%
  mutate(NAME_1_clean = stri_trans_general(NAME_1, "Latin-ASCII"))

mpsz_customers <- mpsz %>%
  left_join(dept_customer, by = c("NAME_1_clean" = "department_clean"))
```

### 3.6.3 Choropleth Mapping Geospatial Data Using *tmap*

```{r}
#| echo: true
#| code-fold: true
#| code-summary: "Code"

library(tmap)

tmap_mode("plot")

tm_shape(mpsz_customers) +
  tm_polygons(
    col = "no_customers",
    border.col = "black",
    palette = "YlOrRd",
    colorNA = "gray90",
    title = "Number of customers"
  ) +
  tm_layout(
    title = "Geographical Distribution of Customers",
    frame = FALSE
  )
```

# 4. Confirmatory Data Analysis

In this section, I will compare the factors that affect churn probability using a parametric method (Chi-square test) and a non-parametric method (Fisher's Exact test).

In the dataset, `churn_probability` is a numerical variable. Therefore, it will be converted into three categories: *low, medium, and high*, using the code chunk below.

```{r}
#| echo: true
#| code-fold: true
#| code-summary: "Code"

library(dplyr)

customer <- customer %>%
  mutate(
    churn_group = cut(
      churn_probability,
      breaks = c(0,0.2,0.3,0.4),
      labels = c("Low","Medium","High"),
      include.lowest = TRUE
    )
  )
```

## 4.1 Churn_probability VS Gender

```{r, fig.width=8, fig.height=10}
#| echo: true
#| code-fold: true
#| code-summary: "Code"

library(ggstatsplot)
p1 <- ggbarstats(customer, gender, churn_group, type="parametric", title = "Parametric")
p2 <- ggbarstats(customer, gender, churn_group, type="nonparametric",title = "Non-parametric")
p1/p2

```

## 4.2 Churn_probability VS Income

```{r, fig.width=8, fig.height=10}
#| echo: true
#| code-fold: true
#| code-summary: "Code"

p3 <- ggbarstats(customer, income_bracket, churn_group, type="parametric", title = "Parametric")
p4 <- ggbarstats(customer, income_bracket, churn_group, type="nonparametric",title = "Non-parametric")
p3/p4

```

## 4.3 Churn_probability VS Education level

```{r, fig.width=8, fig.height=10}
#| echo: true
#| code-fold: true
#| code-summary: "Code"

p5 <- ggbarstats(customer, education_level, churn_group, type="parametric", title = "Parametric")
p6 <- ggbarstats(customer, education_level, churn_group, type="nonparametric",title = "Non-parametric")
p5/p6

```

## 4.4 Churn_probability VS Marital status

```{r, fig.width=8, fig.height=10}
#| echo: true
#| code-fold: true
#| code-summary: "Code"

p7 <- ggbarstats(customer, marital_status, churn_group, type="parametric", title = "Parametric")
p8 <- ggbarstats(customer, marital_status, churn_group, type="nonparametric",title = "Non-parametric")
p7/p8

```

## 4.5 Churn_probability VS Customer segment

```{r, fig.width=8, fig.height=10}
#| echo: true
#| code-fold: true
#| code-summary: "Code"

p9 <- ggbarstats(customer, customer_segment, churn_group, type="parametric", title = "Parametric")
p10 <- ggbarstats(customer, customer_segment, churn_group, type="nonparametric",title = "Non-parametric")
p9/p10

```

## 4.6 Churn_probability VS Savings account

```{r, fig.width=8, fig.height=10}
#| echo: true
#| code-fold: true
#| code-summary: "Code"

p11 <- ggbarstats(customer, savings_account, churn_group, type="parametric", title = "Parametric")
p12 <- ggbarstats(customer, savings_account, churn_group, type="nonparametric",title = "Non-parametric")
p11/p12

```

## 4.7 Churn_probability VS Acquisition channel

```{r, fig.width=8, fig.height=10}
#| echo: true
#| code-fold: true
#| code-summary: "Code"

p13 <- ggbarstats(customer, acquisition_channel, churn_group, type="parametric", title = "Parametric")
p14 <- ggbarstats(customer, acquisition_channel, churn_group, type="nonparametric",title = "Non-parametric")
p13/p14

```

## 4.8 Churn_probability VS Number of active products

```{r, fig.width=8, fig.height=10}
#| echo: true
#| code-fold: true
#| code-summary: "Code"

p15 <- ggbarstats(customer, active_products, churn_group, type="parametric", title = "Parametric")
p16 <- ggbarstats(customer, active_products, churn_group, type="nonparametric",title = "Non-parametric")
p15/p16

```

## 4.9 Churn_probability VS Satisfaction score

```{r, fig.width=8, fig.height=10}
#| echo: true
#| code-fold: true
#| code-summary: "Code"

p17 <- ggbarstats(customer, satisfaction_score, churn_group, type="parametric", title = "Parametric")
p18 <- ggbarstats(customer, satisfaction_score, churn_group, type="nonparametric",title = "Non-parametric")
p17/p18

```

## 4.10 Churn_probability VS Feedback sentiment

```{r, fig.width=8, fig.height=10}
#| echo: true
#| code-fold: true
#| code-summary: "Code"

p19 <- ggbarstats(customer, feedback_sentiment, churn_group, type="parametric", title = "Parametric")
p20 <- ggbarstats(customer, feedback_sentiment, churn_group, type="nonparametric",title = "Non-parametric")
p19/p20
```

## 4.11 Churn_probability VS Customer lifetime value

```{r, fig.width=8, fig.height=10}
#| echo: true
#| code-fold: true
#| code-summary: "Code"

p21 <- ggbarstats(customer, clv_segment, churn_group, type="parametric", title = "Parametric")
p22 <- ggbarstats(customer, clv_segment, churn_group, type="nonparametric",title = "Non-parametric")
p21/p22
```

## 4.12 Churn_probability VS Average login frequency

```{r, fig.width=8, fig.height=10}
#| echo: true
#| code-fold: true
#| code-summary: "Code"

p23 <- ggbarstats(customer, app_logins_group, churn_group, type="parametric", title = "Parametric")
p24 <- ggbarstats(customer, app_logins_group, churn_group, type="nonparametric",title = "Non-parametric")
p23/p24
```

# 5. Reference

<https://www.sciencedirect.com/science/article/pii/S2352340926000375>

<https://giniceseah.netlify.app/posts/2021-07-31-storyboard/>

<https://r4va.netlify.app/chap21>